\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
conclusion

\section{Motivation}
\label{sec:motivation}
Even with an upcoming W3C recommendation, it can be expected that several constraint languages will be used in practice in future -- consider the situation in the XML world, where a standardized schema language was available from the beginning and yet additional ways to formulate and check constraints have been created. Therefore, 
semantically equivalent \emph{specific constraints} represented in different languages will exist.
This raises two questions: 
\begin{enumerate}
 \item How can we ensure that two semantically equivalent constraints are actually validated consistently?
 \item How can we support the transformation of semantically equivalent constraints from one constraint language to another?
\end{enumerate}

\paragraph{Consistent implementation.}
Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the constraint is checked.
Our framework therefore provides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a SPIN mapping
for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}, it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.

@@

The properties describing a simple constrained are very structural. The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be 'REGEX' where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types. Complex constraints again need several constraining elements to be expressed.

Irrespective of and additional to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element. The \emph{context class} limits the constraint to individuals of a specific class. Depending on the constraining elements, a list of \emph{classes} can be provided, for example to determine the valid classes for a value or to define a class intersection to be used in a constraint. \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to. A typical example for a constraint with a right hand side list of properties would be R43, literal value comparison, where constraints like birthDate $<$ deathDate can be expressed.

Finally, the \emph{constraining value} contains a literal value to be checked against; for instance in the case of the 'REGEX' element, it contains the regular expression to be evaluated.

@@

%Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group, 
%we published by today 81 constraint types \cite{BoschNolleAcarEckert2015}
%which form the basis to
%lay the ground for discussions on validation
%by defining a basic terminology and classification system for RDF constraints.

Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
we published by today 81 requirements to validate RDF data and to formulate constraints; 
each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.
These constraint types form the basis to
lay the ground for discussions on validation
by defining a basic terminology and classification system for RDF constraints.
%
There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
Thus, the idea behind this paper is to satisfy all requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
%To show that constraints can either be represented specifically (\emph{specific constraints}) by constraint languages
%or generically (\emph{generic constraints}) by \emph{description logics (DL)},
%we mapped constraint types to DL 
%to determine which DL constructs are needed to express them \cite{BoschNolleAcarEckert2015} (Section \ref{sec:vocabulary}).

As there is no standard way to formulate constraints, 
semantically equivalent \emph{specific constraints} may be represented by a variety of languages - each of them having different syntax and semantics.
We propose transformations between semantically equivalent \emph{specific constraints}
by using the proposed vocabulary to intermediately represent constraints in a generic way
(1) to avoid the necessity to understand several languages,
(2) to resolve misunderstandings about the meaning of particular constraints, and
(3) to enhance the interoperability of constraint languages (Section \ref{sec:transformations}).

We use \emph{SPIN} as basis to develop a validation environment\footref{rdf-validator} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footref{spin-mappings} \cite{BoschEckert2014-2}.
When language designers extend constraint languages 
to be able to formulate constraints of not yet supported constraint types,
our proposal enables to reuse the validation implementation of these constraint types 
by mapping \emph{specific constraints} expressed by the language to the corresponding \emph{generic constraint}.
For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
by providing a \emph{SPIN} mapping
for each constraint type\footref{RDF-CV-2-SPIN}  
whose constraints are represented generically \cite{BoschEckert2015-2}. 
Furthermore, our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
leads to exactly the same validation results, 
i.e., that validation is performed independently from the used language (Section \ref{sec:validation}).

It is part of future work 
(1) to extend the \emph{RDF Validator} by generating \emph{generic constraints} according to inputs of domain experts who may not be familiar with the formulation of constraints,
(2) to offer bidirectional transformations between \emph{specific constraints} expressed by the most common constraint languages and corresponding \emph{generic constraints}, and
(3) to provide translations between semantically equivalent \emph{specific constraints} expressed by the most common constraint languages by using the developed vocabulary to intermediately represent constraints.
Identifying RDF validation requirements is an ongoing process,
so the task to map constraints of new constraint types to the vocabulary.

%\begin{itemize}
	%\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
	%\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
	%\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
%\end{itemize}

>>>>

\section{Motivation}
\label{sec:motivation}
Even with an upcoming W3C recommendation, it can be expected that several constraint languages will be used in practice in future -- consider the situation in the XML world, where a standardized schema language was available from the beginning and yet additional ways to formulate and check constraints have been created. Therefore, 
semantically equivalent \emph{specific constraints} represented in different languages will exist.
This raises two questions: 
\begin{enumerate}
 \item How can we ensure that two semantically equivalent constraints are actually validated consistently?
 \item How can we support the transformation of semantically equivalent constraints from one contraint language to another?
\end{enumerate}

\paragraph{Consistent implementation.}
Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the contraint is checked.
Our framework therefore proides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a \emph{SPIN} mapping
for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}, it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.

@@

The properties describing a simple constrained are very structural. The central property is the \emph{constraining element} which refers to one of 103 contraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be 'REGEX' where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types. Complex constraints again need several constraing elements to be expressed.

Irrespective of and additonal to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element. The \emph{context class} limits the constraint to individuals of a specific class. Depending on the constraining elements, a list of \emph{classes} can be provided, for example to determine the valid classes for a value or to define a class intersection to be used in a constraint. \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to. A typical example for a constraint with a right hand side list of properties would be R43, literal value comparision, where constraints like birthDate $<$ deathDate can be expressed.

Finally, the \emph{constrainig value} contains a literal value to be checked against; for instance in the case of the 'REGEX' element, it contains the regular expression to be evaluated.

@@

In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language. The framework consists of a very simple conceptual model using the RDF Constraints Vocabulary (RDF-CV) which has been introduced in this paper. The core of the framework is the definition of 103 constraining elements that are used to define all 81 types of constraints that to date have been identified within the \emph{DCMI RDF Application Profiles Task Group} and in cooperation with the \emph{W3C Data Shapes Working Group}.
The full definition of all constraint types and the representation of the types in RDF-CV is provided in an accompanying technical report \cite{BoschNolleAcarEckert2015}.

We have demonstrated how the framework can be used to map a constraint language to RDF-CV and also how to map back from RDF-CV to the constraint language. The latter enables the transformation of sematically equivalent constraints from one constraint language to another via the RDF-CV intermediate representation.

We think that this approach is suitable
\begin{enumerate}
  \item to implement the validation of constraints consistently across constraint languages,
  \item to support the extension of constraint languages by means of a simple mapping, and
  \item to enhance or rather establish the interoperability of different constraint languages.
\end{enumerate}

It is part of future work to finalize the implementation of all 81 constraint types in our \emph{RDF Validator}, to fully map constraint languages to RDF-CV (first and foremost DSP and OWL) and of course keep the framework in sync with the ongoing work in the working groups.
